Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-16 Paper2015.tex
Completed first draft text for results section.
Removed some unneeded sections (figures, tables etc.).
Added some todos.

\maketitle % Insert title

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------
\begin{IEEEkeywords}
ANITA,Geant4, neutron,gamma, TSL.
\end{IEEEkeywords}

@@

In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review frst part of Results section -- move to introduction?}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes: CUP}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes: CUP}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}\todo{Add experimental data to TOF figure (CUP)}
	\label{fig:TOFFrameOverlapspectrum}}\\
	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}\todo{Add experimental data to TOF figure (SUP)}
	\label{fig:SUP10FrameOverlapspectrum}}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \hspace{\columnwidth}\todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
        \hspace{\columnwidth}\todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \hspace{\columnwidth}\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \hspace{\columnwidth}\todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

\subsection{Subsection One}
\begin{figure*}[!t]
	\centering
	\subfloat[Geant4 modelling]{\includegraphics[width=3in]{TOFLethargylinearspace.eps}
	\label{fig:TOFLethargylinearspace}}
	\hfil
	\subfloat[TSL MCNPX modelling~\cite{Prokofiev14}]{\includegraphics[width=3in]{StandardLetNYieldAtCUPTOF.eps}
	\label{fig:StandardLethargylinearspace}}
	\caption{Simulated spectral fluence at the CUP-TOF position for \SI{3}{\cm}, \SI{10.2}{\cm}, \SI{30}{\cm} and no collimator. The dashed line, solid line, and dotted line represent the neutron yield of collimator with diameter 3, 10.2, and \SI{30}{\cm}. The dash-dotted line represents modelling with no collimator attached.}
	\label{fig_LethargylinearspaceFor4collimators}
\end{figure*}

Fig.~\ref{fig_LethargylinearspaceFor4collimators} shows

\begin{figure}[!t]
	\centering
	\includegraphics[width=3in]{SUPcomparedlinearspace.eps}
	\caption{Simulated spectral yield at the SUP for \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
	\label{fig:SUPcomparedlinearspace}
\end{figure}

\subsection{Subsection Two}
\begin{figure*}[!t]
	\centering
	\subfloat[Differential]{\includegraphics[width=3in]{DiffYieldComparedSUPCUP10.eps}
	\label{fig:DiffYieldComparedSUPCUP10}}
	\hfil
	\subfloat[Integral]{\includegraphics[width=3in]{IntYieldComparedSUPCUP10.eps}
	\label{fig:IntYieldComparedSUPCUP10}}
	\caption{Comparison of Geant4 simulated spectral fluence with analytical model at the SUP and the CUP with \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
	\label{fig:NYieldComparedSUPCUP10}
\end{figure*}

\subsection{Subsection Three}

\subsection{Subsection Four, time of flight spectrum}

\begin{figure}[!t]
	\centering
	\subfloat[Time of flight spectrum at the CUP-TOF position, with \SI{3}{\cm} collimator]{\includegraphics[width=3in]{TOF3frameoverlap.eps}
	\label{fig:TOFFrameOverlapspectrum}}
	\vfil
	\subfloat[Time of flight spectrum at the SUP, with \SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{SUP10frameoverlap.eps}
	\label{fig:SUP10FrameOverlapspectrum}}
\end{figure}

\subsection{Subsection Five, beam profile folding with $^{238}U(n,f)$ cross-section}

\begin{figure}[!t]
	\centering
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF3beampro.png}
	\label{fig:CUPTOF3beampro}}
	\hfil
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF10beampro.png}
	\label{fig:CUPTOF10beampro}}
	\hfil
	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{CUPTOF30beampro.png}
	\label{fig:CUPTOF30beampro}}
	\caption{Neutron beam profiles folding with $^{238}U(n,f)$ cross-section at the CUP-TOF position with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator}
	\label{fig:CUPTOFbeamprofileFolding}
\end{figure}

\begin{figure}[!t]
	\centering
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=2.5in]{SUP3beamproFolding.png}
	\label{fig:SUP3beamproFolding}}
	\hfill
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=2.5in]{SUP10beamproFolding.png}
	\label{fig:SUP10beamproFolding}}
	\hfill
	\subfloat[\SI{30}{\cm} collimator]{\includegraphics[width=2.5in]{SUP30beamproFolding.png}
	\label{fig:SUP30beamproFolding}}
	\caption{Neutron beam profile folding with $^{238}U(n,f)$ cross-section at the SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimator}
	\label{fig:SUPbeamprofileFolding}
\end{figure}

Fig.~\ref{fig:CUPTOFbeamprofileFolding} shows

%\begin{equation}
%\label{eq:emc}
%e = mc^2
%\end{equation}

\subsection{Gamma, subsection one : Spatial distribution}

\begin{figure}[!t]
	\centering
	\subfloat[\SI{3}{\cm} collimator]{\includegraphics[width=3in]{CUP3ColSpatialDistributionAllG}
	\label{fig:CUP3SpatialDistributionAllG}}
	\hfil
	\subfloat[\SI{10.2}{\cm} collimator]{\includegraphics[width=3in]{CUP10ColSpatialDistributionAllG}
	\label{fig:CUP10SpatialDistributionAllG}}
	\caption{Gamma spatial distribution at the CUP with \SI{3}{\cm}, and \SI{10.2}{\cm} collimator~\cite{Prokofiev2009,Prokofiev14}}
	\label{fig:gCUPSpatialDistribution}
\end{figure}

\begin{table}[!tbp]
\caption[{$\gamma$ yield for each collimator in a radius of \SI{5}{\cm} at the CUP}]{$\gamma$ yield for each collimator at the CUP}	%title of the table
\centering
\label{table:GYieldCUP}
\begin{tabular}{lcc}
	\hline% insert double-line
	Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}  \\
	\cmidrule(r){2-3}
/\si{\cm}       & /\SI{e-6}{\photon\per\cm\squared\per\proton} & /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
\hline % insert single-line
3 & 4.93 & 15.73\\

10.2 & 4.86  &  15.27\\

30 & 4.44  &  13.80\\
\hline
\end{tabular}
\end{table}

\begin{table}[!tbp]
\caption[$\gamma$ yield for each collimator in umbra region at the SUP]{$\gamma$ yield for each collimator in umbra region at the SUP}	%title of the table
\centering
\label{table:GYieldSUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}   \\
\cmidrule(r){2-3}
/\si{\cm}       & \/\SI{e-6}{\photon\per\cm\squared\per\proton} &  /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
\hline % insert single-line
3 & 2.3 & 6.7\\

10.2 & 2.8  &  8.3\\

30 & 3.2  &  9.4\\
\hline
\end{tabular}
\end{table}

\subsection{Gamma, subsection two : Photon spectra at the CUP and SUP }

\begin{figure}[!t]
	\centering
	\subfloat[CUP]{\includegraphics[width=3in]{gCUPDYieldcompared}
	\label{fig:gCUPDYieldcompared}}
	\vfil
	\subfloat[SUP]{\includegraphics[width=3in]{gSUPDYieldcompared}
	\label{fig:gSUPDYieldcompared}}
	\caption{Comparison of differential photon yield at the CUP and SUP}
	\label{fig:gDYieldspectra}
\end{figure}

\begin{figure}[!t]
	\centering
	\subfloat[CUP]{\includegraphics[width=3in]{gCUPIYieldcompared}
	\label{fig:gCUPIYieldcompared}}
	\vfil
	\subfloat[SUP]{\includegraphics[width=3in]{gSUPIYieldcompared}
	\label{fig:gSUPIYieldcompared}}
	\caption{Comparison of integral photon yield at the CUP and SUP}
	\label{fig:gIYieldspectra}
\end{figure}
Figure~\ref{fig:gIYieldspectra} displayed integral photon spectra at the CUP and SUP. The photon spectra at the SUP with \SI{3}{\cm} collimator, it is dominated by energy within about \SI{7}{\MeV} at the SUP, see Figure~\ref{fig:gSUPIYieldcompared}.

\begin{table}
\caption{$\gamma$ dose rate for each collimator at the CUP and SUP}	%title of the table
\centering
\label{Table:DoseRate}
        \begin{tabular}{l c c}
            \toprule
            {collimator diameter}   &{CUP}         &{SUP}\\
            {\si{\centi\metre}}    &{\si{mSvh^{-1}}}   &{\si{mSvh^{-1}}}\\
            \midrule
            3                       & 378.0                	& 17.32\\
            10.2                  & 369.4               	& 20.90\\
            30                     & 336.4          		& 23.65\\
            \bottomrule
\end{tabular}
\end{table}

\begin{figure}[!t]
	\centering
	\subfloat[CUP]{\includegraphics[width=2.5in]{DoseVSenergyCUP.eps}
	\label{fig:DoseVSenergyCUP}}
	\hfil
	\subfloat[SUP]{\includegraphics[width=2.5in]{DoseVSenergySUP.eps}
	\label{fig:DoseVSenergySUP}}
	\caption{Dose versus energy at the CUP and SUP with \SI{3}{\cm}, \SI{10.2}{\cm}, and \SI{30}{\cm} collimators}
	\label{fig:DoseVSenergy}
\end{figure}

%------------------------------------------------
\section{Discussion}

\subsection{Subsection One}

Neutron .....

\subsection{Subsection Two}

Gamma .....

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

@@

>>>>

\maketitle % Insert title
\todo{Check title, affiliations etc.}
%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------

@@

In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.\todo{Review first part of Results section -- move to introduction?}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

@@

\begin{figure}[t]
    \vspace{2in}
	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes: CUP}\hspace{\columnwidth}}\\
    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes: CUP}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\subfloat[At the CUP-TOF position, with \SI{3}{\cm} collimator]{\todo{Add experimental data to TOF figure (CUP)\includegraphics[width=3in]{TOF3frameoverlap.eps}}
	\label{fig:TOFFrameOverlapspectrum}}\\
	\subfloat[At the SUP, with \SI{10.2}{\cm} collimator]{\todo{Add experimental data to TOF figure (SUP)}\includegraphics[width=3in]{SUP10frameoverlap.eps}
	\label{fig:SUP10FrameOverlapspectrum}}
    \caption{Simulated neutron time of flight spectra compared to measurements}
    \label{fig:TOFSpectra}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

@@

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}\hspace{\columnwidth}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}

\section{Discussion}
\todo{Discussion}

@@

\todo{Complete citations}
